Sound Automated Synthesis of Digital Controllers

### 2016-10-10 paper/paper.tex
Changes on section 2

\begin{myassumption}
%
The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
be disregarded. Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  may be considered a sufficient discrete-time representation of $G(s)$.
%
\end{myassumption}

@@

@@

Since the controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
\end{align}
we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
\begin{align}
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.

>>>>

\begin{myassumption}
%
\label{assumption:cont_and_plant}
The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
be disregarded. Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  may be considered a sufficient discrete-time representation of $G(s)$.
%
\end{myassumption}

@@

%------------------------------------
\subsection{On the stability considering effects of implementation issues and quantization noises}
\label{sec:stability}
%------------------------------------

In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantization noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$ and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the following equation may written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}.

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{internal_stab_lemma}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq_int_stab}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{NFWL[_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}

@@

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
\end{align}
we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
\begin{align}
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.
